Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-02 Paper.tex
Copied and pasted a formula with tiny in math mode to l. 2097 to see if it will pick up in the Travis CI build.

The proof-of-concept series includes a development premine, making the state root hash some value $stateRoot$. Also \hyperlink{H s}{$time$} will be set to the initial timestamp of the genesis block. The latest documentation should be consulted for those values.$\mathtt{\tiny KEC}\big(\mathtt{\tiny RLP}\big( () \big)\big)$

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

>>>>

The proof-of-concept series includes a development premine, making the state root hash some value $stateRoot$. Also \hyperlink{H s}{$time$} will be set to the initial timestamp of the genesis block. The latest documentation should be consulted for those values.

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:$\mathtt{\tiny KEC}\big(\mathtt{\tiny RLP}\big( () \big)\big)$
